Meshpoint optimization

### 2022-04-22 notes/optimizing meshpoints.Rmd
add more notes for github pages

```{r data, echo=TRUE}
tar_load(vit_list_det_ff)
tar_load(vit_list_stoch_ff)
```

@@

###Note:

@@

```{r}
lambdas_stoch <-
  proto_stoch_list %>%
  map_dbl( ~ make_ipm(
    .x,
    iterations = 100,
    kernel_seq = year_seq,
    usr_funs = list(get_scat_params = get_scat_params, coef = coef)
  ) %>% lambda(log = FALSE))

>>>>

```{r data, echo=TRUE}
withr::with_dir(here::here(), {
  tar_load(vit_list_det_ff)
  tar_load(vit_list_stoch_ff)
})
```

@@

### Note:

@@

```{r eval=FALSE}
lambdas_stoch <-
  proto_stoch_list %>%
  map_dbl( ~ make_ipm(
    .x,
    iterations = 100,
    kernel_seq = year_seq,
    usr_funs = list(get_scat_params = get_scat_params, coef = coef)
  ) %>% lambda(log = FALSE))
